---
title: "R Notebook"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("lubridate")
library("caret")
```

```{r}
dfc <- read_csv("assignment3Carvana.csv")
```

```{r}
skim(dfc)
```

```{r}
set.seed(52156) 
dfcTrain <- dfc %>% sample_frac(0.65) 
dfcTest <- dplyr::setdiff(dfc,dfcTrain)
```


```{r}
str(dfcTrain)
```
Question 2) (a)
```{r}
plot1 <- dfcTrain %>% ggplot(aes(x= BadBuy, y=MMRAauction, group= BadBuy)) + geom_boxplot() 
plot1
```

```{r}
plot2 <- dfcTrain %>% ggplot(aes(x= BadBuy, y=Age, group= BadBuy)) + geom_boxplot() 
plot2
```

```{r}
plot3 <- dfcTrain %>% ggplot(aes(x= BadBuy, y=Odo, group= BadBuy)) + geom_boxplot() 
plot3
```

Question 2) (b)
```{r}
dfcTrain %>% 
  group_by(Size) %>% 
  summarise("Lemons" = sum(BadBuy), "GoodCars" = length(BadBuy)- sum(BadBuy), "PercentLemon" = Lemons/length(BadBuy)*100, "PercentGoodCars" = GoodCars/length(BadBuy)*100) %>% 
  arrange(desc(PercentLemon),desc(PercentGoodCars))
```

Question 3) (a)
```{r}
fitLmTrain <- 
  lm(BadBuy~.,data= dfcTrain) %>% 
  predict(.,dfcTrain) %>% 
  bind_cols(dfcTrain, predictedBadBuy = .)

fitLmTrain 
```

```{r}
fitLmTest <- 
  lm(BadBuy~.,data= dfcTrain) %>% 
  predict(.,dfcTest) %>% 
  bind_cols(dfcTest, predictedBadBuy = .)

fitLmTest 
```


```{r}
perfTrain <- metric_set(rmse, mae)
perfTrain(fitLmTrain, truth= BadBuy, estimate= predictedBadBuy )
```

```{r}
perfTest <- metric_set(rmse, mae)
perfTest(fitLmTest, truth= BadBuy, estimate= predictedBadBuy )
```
Question 3) (c)
```{r}

modellm <- lm(BadBuy ~., data= dfcTrain)

resultslm <- 
  modellm %>% 
  predict(dfcTest, type= "response") %>% 
  bind_cols(dfcTest,predictedBadBuy=.) %>% 
  mutate(predictedBadBuy = as.factor(ifelse(predictedBadBuy > 0.5,1,0)))


resultslm
```

```{r}
resultslm$BadBuy <- as.factor(resultslm$BadBuy)
```


```{r}
resultslm %>% 
  conf_mat(truth= BadBuy, estimate= predictedBadBuy) %>% 
  autoplot(type= "heatmap")
```
Question 3) (d)
```{r}
accuracyConfMatrix <- 
  resultslm %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive = '1')

accuracyConfMatrix
```
```{r}
newdf<- data.frame(Auction="ADESA",	Age=1,Make="HONDA",Color="SILVER",WheelType="Covers",Odo=10000,Size="LARGE",MMRAauction=8000,MMRAretail=10000)
predict(modellm, newdata=newdf)
```

Question 4) (a)
```{r}
dfcTrain$BadBuy <- as.factor(dfcTrain$BadBuy)
dfcTest$BadBuy <- as.factor(dfcTest$BadBuy)
```

```{r}
modelglm <-
  train(BadBuy~., family= "binomial", data= dfcTrain, method= 'glm')
```

```{r}
library(plyr)

unique(dfc$Color)
dfc$Color <- revalue(dfc$Color, c("NOTAVAIL"="NULL"))
unique(dfc$Color)
```

```{r}
unique(dfc$Make)
```

```{r}
dfc %>% 
  group_by(Make) %>% 
  tally(name = 'Count')
```

```{r}
dfc$Make <- revalue(dfc$Make, c("ACURA"="OTHER", "CADILLAC"="OTHER","LEXUS"="OTHER","MINI"="OTHER","SUBARU"="OTHER","VOLVO"="OTHER"))
dfc$BadBuy <- as.factor(dfc$BadBuy)
```

```{r}
set.seed(52156) 
dfcTrain2 <- dfc %>% sample_frac(0.65) 
dfcTest2 <- dplyr::setdiff(dfc,dfcTrain)
```

```{r}
modelGLM <-
  train(BadBuy~., family= "binomial", data= dfcTrain2, method= 'glm') 

resultsglm2 <-
modelGLM %>%
  predict(dfcTest2, type= "raw") %>% 
  bind_cols(dfcTest2,predictedBadBuy=.)

resultsglm2
```

```{r}
summary(modelGLM)
```
Question 4) (d)
```{r}
confglm2 <- resultsglm2 %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive = '1')

confglm2
```

Question 4) (e)
```{r}

predict(modelGLM, newdata=newdf)
```

Question 5)
```{r}
set.seed(123)
modelLDA  <-
    train(BadBuy ~ ., data= dfcTrain2, method= 'lda',trControl=trainControl(method='cv', number=10))
summary(modelLDA)
```

```{r}
resultsLda <- 
    modelLDA %>% 
    predict(dfcTest2, type= 'raw') %>%      
    bind_cols(dfcTest2, predictedBadBuy=.) 
resultsLda
```

```{r}
resultsLda %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive = '1')
```


Question 5) (b)
```{r}
set.seed(123)
modelknn  <-
    train(BadBuy ~ ., data= dfcTrain2, method= 'knn', trControl=trainControl(method='cv', number=10), tuneLength=20, preProcess=c("center","scale"))
summary(modelknn)
```


```{r}
resultsKNN <-
  modelknn %>% 
  predict(dfcTest2, type= "raw") %>% 
  bind_cols(dfcTest2,predictedBadBuy=.)
```

```{r}
knnConfMatrix <- 
  resultsKNN %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive = '1')

knnConfMatrix
```

```{r}
plot(modelknn)
```


```{r}
modelknn$bestTune
```

Question 5) (c)
```{r}
lambdaValues <- 10^seq(-5, 2, length = 100)
set.seed(123)

modelLasso <- 
  train(BadBuy ~ ., family='binomial', data=dfcTrain2, method='glmnet', trControl=trainControl(method='cv', number=10), tuneGrid = expand.grid(alpha=1, lambda=lambdaValues))

summary(modelLasso)
```


```{r}
resultsLasso <- 
  predict(modelLasso,dfcTest2, type= 'raw') %>%
  bind_cols(dfcTest2, predictedBadBuy=.)
```

```{r}
varImp(modelLasso)$importance %>%    # Add scale=FALSE inside VarImp if you don't want to scale
  rownames_to_column(var = "Variable") %>%
  mutate(Importance = scales::percent(Overall/100)) %>% 
  arrange(desc(Overall)) %>% 
  as_tibble()
```

```{r}
#Variable importance plot with the most important variables
plot(varImp(modelLasso), top = 25)    # Add top = XX to change the number of visible variables
```

```{r}
#Optimum lambda selected by the algorithm
modelLasso$bestTune$lambda   # You can also run fitLasso$finalModel$lambdaOpt
```
```{r}
resultsLasso %>% 
  conf_mat(truth = BadBuy , estimate = predictedBadBuy) %>% 
  autoplot(type = 'heatmap')
```
```{r}
resultsLasso %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive='1')
```

Question 5) (d)
```{r}
lambdaValues <- 10^seq(-5, 2, length = 100)
set.seed(123)

modelRidge <- 
  train(BadBuy ~ ., family='binomial', data=dfcTrain2, method='glmnet', trControl=trainControl(method='cv', number=10), tuneGrid = expand.grid(alpha=0, lambda=lambdaValues))

summary(modelRidge)
```


```{r}
resultsRidge <- 
  predict(modelRidge,dfcTest2, type= 'raw') %>%
  bind_cols(dfcTest2, predictedBadBuy=.)
```

```{r}
resultsRidge %>% 
  conf_mat(truth = BadBuy , estimate = predictedBadBuy) %>% 
  autoplot(type = 'heatmap')
```

```{r}
resultsRidge %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive='1')
```


```{r}
lambdaValues <- 10^seq(-5, 2, length = 100)
set.seed(123)

modelElasticNet <- 
  train(BadBuy ~ ., family='binomial', data=dfcTrain2, method='glmnet', trControl=trainControl(method='cv', number=10), tuneGrid = expand.grid(alpha=0.5, lambda=lambdaValues))

summary(modelElasticNet)
```

```{r}
resultsElasticNet <- 
  predict(modelElasticNet,dfcTest2, type= 'raw') %>%
  bind_cols(dfcTest2, predictedBadBuy=.)
```

```{r}
resultsElasticNet %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive='1')
```

Question 5) (e)
```{r}
set.seed(123)
modelQDA  <-
    train(BadBuy ~ ., data= dfcTrain2, method= 'qda',trControl=trainControl(method='cv', number=10))

summary(modelQDA)
```


```{r}
resultsQDA <- 
  predict(modelQDA,dfcTest2, type= 'raw') %>%
  bind_cols(dfcTest2, predictedBadBuy=.)
```


```{r}
resultsQDA %>% 
  xtabs(~BadBuy + predictedBadBuy, .) %>% 
  confusionMatrix(positive='1')
```

Question 5) (f)

```{r}
resultsLDAProb <- bind_cols(dfcTest2,modelGLM %>%  predict(dfcTest2, type='prob') )%>%mutate(model="LDA")
resultsKNNProb <- bind_cols(dfcTest2,modelLDA %>%  predict(dfcTest2, type='prob') )%>%mutate(model="kNN")
resultsLassoProb <- bind_cols(dfcTest2,modelLasso %>%  predict(dfcTest2, type='prob') )%>%mutate(model="Lasso")
resultsRidgeProb <- bind_cols(dfcTest2,modelRidge %>%  predict(dfcTest2, type='prob') )%>%mutate(model="Ridge")
resultsElasticNetProb <- bind_cols(dfcTest2,modelElasticNet %>%  predict(dfcTest2, type='prob') )%>%mutate(model="ElasticNet")
resultsQDAProb <- bind_cols(dfcTest2,modelQDA %>%  predict(dfcTest2, type='prob') )%>%mutate(model="QDA")
```


```{r}
library(cowplot)
glmOutAll <- bind_rows(resultsLDAProb, resultsKNNProb, resultsLassoProb, resultsRidgeProb, resultsElasticNetProb, resultsQDAProb)


glmOutAll %>%
  group_by(model) %>% # group to get individual ROC curve for each model
  roc_curve(truth = BadBuy, '1') %>% # get values to plot an ROC curve
  ggplot(aes(x = 1 - specificity, y = sensitivity, color = model)) + # plota ROC curve for each model
  geom_line(size = 1.1) +
  geom_abline(slope = 1, intercept = 0, size = 0.4) +
  coord_fixed() +
  theme_cowplot()
```

```{r}
glmOutAll %>%
  group_by(model) %>% # group to get individual AUC value for each model
  roc_auc(truth = BadBuy, '1')
```

Bonus Question:
```{r warning= FALSE}
library(grplasso)

dfcTrainGroup <-
  dfcTrain2 %>%
  mutate(BadBuy = as.numeric(BadBuy)) %>% 
  mutate(BadBuy = ifelse(BadBuy == 2, 1, 0))
```

```{r warning= FALSE}
set.seed(123)

modelGroupedLasso <- grplasso(BadBuy ~ ., data=dfcTrainGroup, model=LogReg(), lambda=50)
modelGroupedLasso$coefficients
```

```{r warning= FALSE}
set.seed(123)
modelGroupedLasso1 <- grplasso(BadBuy ~ ., data=dfcTrainGroup, model=LogReg(), lambda=100)

modelGroupedLasso1$coefficients

```



