---
title: "R Notebook"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
setwd("C:/") #Don't forget to set your working directory before you start!

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("caret")
```


```{r}
dff= read_csv("lab3FraminghamHeart.csv")
```

```{r}
colsToFactor <- c('gender', 'education', 'currentSmoker', 'BPMeds', 'prevalentStroke', 'prevalentHyp', 'diabetes')
```


```{r}
dff <- dff %>%
  mutate_at(colsToFactor, ~factor(.))
```


```{r}
str(dff)
```
Question 1) 
#sysBP Boxplot
```{r}
plot1 <- dff %>%  
  ggplot(aes(x= TenYearCHD, y=sysBP, group= TenYearCHD)) + 
  geom_boxplot()

plot1

```
#diaBP Boxplot
```{r}
plot2 <- dff %>%  
  ggplot(aes(x= TenYearCHD, y=diaBP, group= TenYearCHD)) + 
  geom_boxplot()

 plot2
```
#totChol Boxplot
```{r}
plot3 <- dff %>%  
  ggplot(aes(x= TenYearCHD, y=totChol, group= TenYearCHD)) + 
  geom_boxplot()
 

plot3
```
Question 2) (i)
```{r}
set.seed(123)

dffTrain <- dff %>%  sample_frac(0.7)
dffTest <- dplyr::setdiff(dff,dffTrain)
```

Question 2) (ii) 
```{r}
#Gender
dffTrain %>% group_by(gender) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))

```

```{r}
#Gender
dffTest %>% group_by(gender) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))
```


```{r}
#AgeGroup
dffTrain %>% group_by( ageGroup=cut_interval(age, length=10)) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))
```


```{r}
#AgeGroup
dffTest %>% group_by( ageGroup=cut_interval(age, length=10)) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))

```
#Histogram
```{r}
plot4 <- dffTrain %>% 
  ggplot(aes(x=age, fill=gender)) +
  geom_histogram(color='black')

plot4

```

Question 3)
```{r}
fitLPM <- lm(TenYearCHD ~., data= dffTrain)
summary(fitLPM)
```

# By logic:  currentSmoker and cigsPerDay are collinear can if cigsPerDay >0 then person is a smoker
# By analysis: Using VIF 
```{r}
car::vif(fitLPM)
```

#Correct model will not have both cigsPerDay and currentSmoker variables. 
# The new model can be made now
```{r}
newfitLPM <- lm(TenYearCHD ~. -currentSmoker, data= dffTrain)
summary(newfitLPM)
```
```{r}
plot(newfitLPM)
```

Question 4)
```{r}
resultsLPM <-
    lm( TenYearCHD ~. -currentSmoker, data= dffTrain ) %>%
    predict(., dffTest) %>%      
    bind_cols(dffTest, predictedProb=.) %>%      
    mutate(predictedClass = ifelse(predictedProb > 0.5, 1, 0))
resultsLPM

```

```{r}
#TenYearCHD in Test data
dffTest %>% group_by(TenYearCHD ) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))
```


```{r}
#TenYearCHD in resultsLPM
resultsLPM %>% group_by(predictedClass ) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))
```

```{r}
#Factoring TenYearCHD in training and test datasets

colsToFactor <- c('TenYearCHD')

dffTrain  <- dffTrain  %>%
  mutate_at(colsToFactor, ~factor(.))
dffTrain

dffTest   <- dffTest   %>%
  mutate_at(colsToFactor, ~factor(.))
dffTest 

```
Question 5)
```{r}
fitGLM <- glm(TenYearCHD ~. -currentSmoker, family = binomial(), data= dffTrain)
summary(fitGLM)
exp(coef(fitGLM))

```
Question 6)
```{r}

#predictedClass will need to be defined as a factor 

resultsLog  <-
    glm(TenYearCHD ~. -currentSmoker, family = binomial(), data= dffTrain ) %>%
    predict(dffTest, type= 'response') %>%      
    bind_cols(dffTest, predictedProb=.) %>%      
    mutate(predictedClass = as.factor(ifelse(predictedProb > 0.5, 1, 0)))
resultsLog 
```

```{r}
resultsLog %>% group_by(predictedClass ) %>%
  tally() %>% 
  mutate(pct = 100*n/sum(n))
```

Question 7)
```{r}
resultsLog %>%
  conf_mat(estimate = predictedClass, truth =TenYearCHD) %>% 
  autoplot(type = 'heatmap')

```
Question 8)
```{r}
#Age vs predictedClass
plot5 <- resultsLog %>%  
  ggplot(aes(x= age, y=predictedProb, color=gender)) + 
  geom_point() +
  geom_smooth()+
  labs(title= "Age vs. Predicted Probability", x= "Age", y= "Predicted Probability")

plot5

```

```{r}
#cigsPerDay vs predictedClass
plot6 <- resultsLog %>%  
  ggplot(aes(x= cigsPerDay, y=predictedProb, color=gender)) + 
  geom_point() +
  geom_smooth() +
  labs(title= "Cigerrates per day vs. Predicted Probability", x= "Cigerrates per day", y= "Predicted Probability")

plot6
```


```{r}
#totChol vs predictedClass
plot7 <- resultsLog %>%  
  ggplot(aes(x= totChol, y=predictedProb, color=gender)) + 
  geom_point() +
  geom_smooth() +
  labs(title= "Total Cholestrol vs. Predicted Probability", x= "Total Cholestrol", y= "Predicted Probability")

plot7
```

```{r}
#glucose vs predictedClass
plot8 <- resultsLog %>%  
  ggplot(aes(x= glucose, y=predictedProb,color=gender)) + 
  geom_point() +
  geom_smooth() +
  labs(title= "Glucose vs. Predicted Probability", x= "Glucose", y= "Predicted Probability")

plot8
```

Question 9)
```{r}
library(e1071)
resultsLogCaret  <-
    train(TenYearCHD ~. -currentSmoker, family = 'binomial', data= dffTrain, method= 'glm' ) %>%
    predict(dffTest, type= 'raw') %>%      
    bind_cols(dffTest, predictedClass=.)  

resultsLogCaret
    
resultsLogCaret %>% 
  xtabs(~predictedClass+TenYearCHD, .) %>% 
  confusionMatrix(positive = '1')

```

Question 10)
```{r}
dff1= read_csv("lab3BancoPortugal.csv")
str(dff1)
```

```{r}
#Converting categorical variables to Factors
colsToFactor <- c('openedAccount', 'newcustomer', 'agegroup', 'job', 'marital', 'education', 'default', 'housing', 'loan', 'contact', 'month', 'day_of_week', 'poutcome')
dff1 <- dff1 %>%
  mutate_at(colsToFactor, ~factor(.))
str(dff1)
```


```{r}
#Splitting into train and test datasets
set.seed(123)

dff1Train <- dff1 %>%  sample_frac(0.7)
dff1Test <- dplyr::setdiff(dff1,dff1Train)
```


```{r}
# Model 1: glm model
#Using all variables except duration

bancoDflog <- glm(openedAccount~. -(duration),family='binomial',data=dff1Train)
summary(bancoDflog)

```


```{r}
#Model 1: Caret
#Using all variables except duration

bancoDflogCaret  <-
    train(openedAccount ~. -duration, family = 'binomial', data= dff1Train, method= 'glm' ) %>%
    predict(dff1Test, type= 'raw') %>%      
    bind_cols(dff1Test, predictedClass=.)  
    
bancoDflogCaret %>% 
  xtabs(~predictedClass+openedAccount, .) %>% 
  confusionMatrix(positive = '1')

```
```{r}
# Model 2: caret model
#Applying domain knowledge and statistical analysis
bancoDflogCaret1  <-
    train(openedAccount ~. -(duration + marital + euribor3m + newcustomer + contact+ education + loan + day_of_week), family = 'binomial', data= dff1Train, method= 'glm' ) %>%
    predict(dff1Test, type= 'raw') %>%      
    bind_cols(dff1Test, predictedClass=.)  
bancoDflogCaret1 %>% 
  xtabs(~predictedClass+openedAccount, .) %>% 
  confusionMatrix(positive = '1')

```

```{r}
# Model 3: caret model 
#Using an irrelevant variaable

bancoDflogCaret2  <-
    train(openedAccount ~ marital, family = 'binomial', data= dff1Train, method= 'glm' ) %>%
    predict(dff1Test, type= 'raw') %>%      
    bind_cols(dff1Test, predictedClass=.)  
    
bancoDflogCaret2 %>% 
  xtabs(~predictedClass+openedAccount, .) %>% 
  confusionMatrix(positive = '1')

```

