---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document:
    latex_engine: xelatex
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
setwd("C:/") #Don't forget to set your working directory before you start!

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
library("lubridate")
library("car")
```

```{r}
dfw <- read_csv("walmartSales.csv")
dfw
```

Q1)
```{r}
fit <- lm(Weekly_Sales~CPI, data= dfw)
summary(fit)
```
Q2)
```{r}
plot1 <- dfw %>% 
  group_by(Store) %>% 
  filter(Store == 10) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot1
```


```{r}
plot2 <-dfw %>% 
  group_by(Store) %>% 
  filter(Store == 11) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot2
```


```{r}
plot3 <- dfw %>% 
  group_by(Store) %>% 
  filter(Store == 12) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot3
```


```{r}
plot4 <- dfw %>% 
  group_by(Store) %>% 
  filter(Store == 13) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot4
```

Q3)
```{r}
plot5 <- dfw %>% 
  filter(year(Date) == 2012) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot5
```

Q4)
```{r}
plot6 <- dfw %>% 
  group_by(Store) %>% 
  filter(Store ==1, year(Date) == 2010) %>% 
  ggplot(aes(x= CPI, y= Weekly_Sales)) +
  geom_point()+
  geom_smooth(method= lm)

plot6
```

Q5)
```{r}
fitCPISize <- lm(Weekly_Sales~CPI + Size,  data= dfw)
summary(fitCPISize)
anova(fit,fitCPISize)
```
Q7)
```{r}
fitFull <- lm(Weekly_Sales~.-Store-Date,  data= dfw)
summary(fitFull)
anova(fitCPISize,fitFull)

```
Q8)
```{r}
fitFullTemp <- lm(Weekly_Sales~.-Store-Date + I(Temperature^2),  data= dfw)
summary(fitFullTemp)
```


```{r}
dfw %>% 
  ggplot(aes(x = Temperature, y = Weekly_Sales)) +  
  geom_smooth(method = lm, formula = y ~ x + I(x^2))

```
Q9) (a) & (b)
```{r}
set.seed(333)
dfwTrain <- dfw %>% sample_frac(0.8)
dfwTest <- dplyr::setdiff(dfw, dfwTrain) 
```

Q9) (c)
```{r}
fitOrg  <- lm(Weekly_Sales~.-Store -Date + I(Temperature^2),  data= dfwTrain)
summary(fitOrg)
```


```{r}
tidy(fitOrg)
```

Q9) (d)
```{r}
resultsOrg <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrg, dfwTest))

resultsOrg
```

Q9) (e)
```{r}
# Calculating the performance measures
performance <- metric_set(rmse, mae)
performance(resultsOrg, truth= Weekly_Sales, estimate= predictedSales )

```

Q9) (f)
```{r}
#Running the model using Date 
fitOrgDate  <- lm(Weekly_Sales~.-Store + I(Temperature^2),  data= dfwTrain)
summary(fitOrgDate)
```



```{r}
#Running the model of test data
resultsOrgDate <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrgDate, dfwTest))
resultsOrgDate
```


```{r}
# Calculating the performance measures 
performance <- metric_set(rmse, mae)
performance(resultsOrgDate, truth= Weekly_Sales, estimate= predictedSales )
```

Q9) (g)
```{r}
#Making the model
fitOrgNoUn  <- lm(Weekly_Sales~.-Store-Date-Unemployment + I(Temperature^2),  data= dfwTrain)
summary(fitOrgNoUn)
```


```{r}
#Running the model on test data
resultsOrgNoUn <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrgDate, dfwTest))
resultsOrgNoUn
```


```{r}
# Calculating the performance measures
performance <- metric_set(rmse, mae)
performance(resultsOrgNoUn, truth= Weekly_Sales, estimate= predictedSales )
```

Q10)
```{r}
#Setting the seed and splitting the data
set.seed(333)
dfwTrain <- dfw %>% sample_frac(0.8)
dfwTest <- dplyr::setdiff(dfw, dfwTrain)

```


```{r}
#Building model on training data
fitLog <- lm(log(Weekly_Sales)~.,  data= dfwTrain)
summary(fitLog)
```


```{r}
#Testing model on testing data
resultsLog <- dfwTest %>%
  			mutate(predictedSales = predict(fitLog, dfwTest))
resultsLog
```


```{r}
#Calculating the performance measures
performance <- metric_set(rmse, mae)
performance(resultsLog, truth= log(Weekly_Sales), estimate= predictedSales)    #log(weeksly sales) to be used here?
```


```{r}
#Comparison between models
anova(fitLog ,fitOrg)
```

Bonus Question
```{r}
bonusDfw <- dfw %>% 
  mutate(salesPerSqFoot = Weekly_Sales/Size)
bonusDfw
```


```{r}
set.seed(333)

dfwTrainBonus <- bonusDfw %>% 
  sample_frac(0.8)

dfwTestBonus <- dplyr::setdiff(bonusDfw, dfwTrainBonus)

```
