---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document:
    latex_engine: xelatex
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.

***

Let's first Load all the required libraries
```{r}
#setwd("C:/Data Mining") #Don't forget to set your working directory before you start!

library("tidyverse")
library("fpp3")
library("plotly")
library("skimr")
library("lubridate")

```


Creating tsibbles
```{r}
month <- as_tibble(yearmonth(seq(as.Date("1991-07-01"), as.Date("2008-06-01"), by = "1 month"))) %>% 
  rename(month=value)
tsDia <- read_csv('antidiabetic.csv') %>%
  bind_cols(month) %>% 
  select(month, drugSales = value) %>%
  as_tsibble(index = month)

tsBoston <-
  boston_marathon %>% 
  filter(Event == "Men's open division") %>%
  select(Year, Time) %>%
  as_tsibble()

tsGas <-us_gasoline

tsEmployment <-
  us_employment %>% 
  filter(Title == "Retail Trade", Month >= '1980-01-01') %>%
  select(Month, Employed)

tsEcon <- us_change %>% 
  filter(Quarter >= '1980-01-01') %>%
  select(Quarter, Consumption)

tsAcc <-
  as_tsibble(USAccDeaths) %>% 
  rename(numOfAccDeaths = value)

set.seed(333)
noise <- tsibble(sample = 1:100, Noise = rnorm(100), index = sample)

tsEmployment

```

# Simple prediction (forecasting) tools

## Naive forecast

```{r}
plotEmpSNaive <-
  tsEmployment %>%
  model(SNAIVE(Employed)) %>%
  forecast(h = "5 years") %>%
  autoplot(tsEmployment, colour = "#769ECB") + #level = NULL,
  geom_line(linetype = 'dashed', colour = '#000000') +
  xlab("Year (monthly data)") + ylab("Number of employed in retail (000)") +
  ggtitle("U.S. retail employment data")
plotEmpSNaive

```

## Drift forecast

```{r}
plotEmpDrift <-
  tsEmployment %>%
  model(RW(Employed ~ drift())) %>%
  forecast(h = "5 years") %>%
  autoplot(tsEmployment, colour = "#769ECB") + #level = NULL,
  geom_line(linetype = 'dashed', colour = '#000000') +
  xlab("Year (monthly data)") + ylab("Number of employed in retail (000)") +
  ggtitle("U.S. retail employment data")
plotEmpDrift

```

# Multiple regression for time series

## Regression for antidiabetic drug sales

```{r}
fitDia <-
  tsDia %>%
  model(TSLM(drugSales ~ trend() + season()))
report(fitDia)

```

## Regression plot with fitted values
```{r}
fitDia
```

```{r}
tsDia
```

```{r}
fitDiaFitted <-
  augment(fitDia) %>%
  ggplot(aes(x = month)) +
  geom_line(aes(y = drugSales, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  xlab("Year") + ylab("Total prescriptions ($ million)") +
  ggtitle("Antidiabetic drug sales") +
  scale_x_date(date_breaks = "years" , date_labels = "%y") +
  guides(colour=guide_legend(title=NULL))
ggplotly(fitDiaFitted)

```

## Regression plot with predictions

```{r}
plotDiaPredicted <-
  tsDia %>%
  model(TSLM(drugSales ~ trend() + season())) %>%
  forecast(h = "5 years") %>%
  autoplot(tsDia, colour = "#769ECB") + #level = NULL,
  geom_line(linetype = 'dashed', colour = '#000000') +
  xlab("Year") + ylab("Total prescriptions ($ million)") +
  ggtitle("Antidiabetic drug sales") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")
plotDiaPredicted

```

## Regression with trend and season for U.S. consumption

```{r}
fitEcon <-
  tsEcon %>%
  model(TSLM(Consumption ~ trend() + season()))
report(fitEcon)

```

## Regression diagnostics (residuals) for the model above

```{r}
fitEcon %>% gg_tsresiduals()

```

## Regression predictive modeling with trend and season (Train/Test split)
```{r}
us_change
```

```{r}
plotEconPredicted <-
  us_change %>%
  filter(Quarter < '2011-01-01') %>%
  model(TSLM(Consumption ~ trend() + season())) %>%
  forecast(new_data = us_change %>% filter(Quarter >= '2011-01-01')) %>%
  autoplot(us_change, colour = "#960A0A") +
  geom_line(colour = '#535353') +
  xlab("Year (quarterly data)") + ylab("Percentage changes in personal consumption") +
  ggtitle("U.S. personal consumption data")
plotEconPredicted

```

## Additional features/predictors for U.S. consumption

```{r}
consumptionFullData <-
  us_change %>%
  gather("Measure", "Change", Consumption, Income, Savings, Unemployment) %>%
  ggplot(aes(x = Quarter, y = Change, colour = Measure)) +
  geom_line() +
  facet_grid(vars(Measure), scales = "free_y") +
  ylab("") + xlab("Year") +
  guides(colour="none") +
  theme(legend.position='none')
ggplotly(consumptionFullData)

```

## Multiple regression for U.S. consumption

```{r}
fitEconOthers <-
  us_change %>%
  model(TSLM(Consumption ~ Income + Savings + Unemployment))
report(fitEconOthers)

```

## Residuals for the model above

```{r}
fitEconOthers %>% gg_tsresiduals()

```

## Regression predictive modeling with other features/predictors (Train/Test split)

```{r}
plotEconOthersPredicted <-
  us_change %>%
  filter(Quarter < '2011-01-01') %>%
  model(TSLM(Consumption ~ Income + Savings + Unemployment)) %>%
  forecast(new_data = us_change %>% filter(Quarter >= '2011-01-01')) %>%
  autoplot(us_change, colour = "#960A0A") + #level = NULL,
  geom_line(colour = '#535353') +
  xlab("Year (quarterly data)") + ylab("Percentage changes in personal consumption") +
  ggtitle("U.S. personal consumption data")
plotEconOthersPredicted

```

## Regression with all (trend, season, and other features/variables)

```{r}
fitEconAll <-
  us_change %>%
  model(TSLM(Consumption ~ trend() + season() + Income + Savings + Unemployment))
report(fitEconAll)

```

## Residuals for the model above

```{r}
fitEconAll %>% gg_tsresiduals()

```

## Regression predictive modeling with trend, season, and additional features (Train/Test split)

```{r}
plotEconAllPredicted <-
  us_change %>%
  filter(Quarter < '2011-01-01') %>%
  model(TSLM(Consumption ~ trend() + season() + Income + Savings + Unemployment)) %>%
  forecast(new_data = us_change %>% filter(Quarter >= '2011-01-01')) %>%
  autoplot(us_change, colour = "#960A0A") + #level = NULL,
  geom_line(colour = '#535353') +
  xlab("Year (quarterly data)") + ylab("Percentage changes in personal consumption") +
  ggtitle("U.S. personal consumption data")
plotEconAllPredicted

```

## Split for good

```{r}
set.seed(333)
tsEconTrain <- us_change %>% filter(Quarter < '2011-01-01')
tsEconTest <- us_change %>% filter(Quarter >= '2011-01-01')

```

## Several models trained and run on test data for predictions to be evaluated/compared

```{r}
tsEconFitAll <-
  tsEconTrain %>%
  model(
    model1TimeTrendAndSeason = TSLM(Consumption ~ trend() + season()),
    model2TimeTrend = TSLM(Consumption ~ trend()),
    model3OtherFeatures = TSLM(Consumption ~ Income + Savings + Unemployment),
    model4TimeTrendAndOthers = TSLM(Consumption ~ trend() + Income + Savings + Unemployment),
    model5TimeTrendAndOthersKnot = TSLM(Consumption ~ trend(knots = c(1980)) + Income + Savings + Unemployment)
  )

tsEconPredictAll <-
  tsEconFitAll %>%
  forecast(new_data = tsEconTest)

tsEconPredictAll

accuracy(tsEconPredictAll, tsEconTest)

```

# ARIMA models

## Revisiting ACF for antidiabetic drug sales

```{r}
plotDiaACF <-
  tsDia %>%
  ACF(drugSales, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the antidiabetic drug sales data")
plotDiaACF

```

## ACF for antidiabetic drug sales after differencing

```{r}
plotDiaDiffACF <-
  tsDia %>%
  mutate(diffdrugSales = difference(drugSales)) %>%
  ACF(diffdrugSales, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the antidiabetic drug sales data")
plotDiaDiffACF

```

## Have we done it right?

```{r}
tsDia %>%
  features(drugSales, unitroot_ndiffs)

```

## Are you sure?

```{r}
tsDia %>%
  features(difference(drugSales), unitroot_ndiffs)

```

## What about seasons?

```{r}
tsDia %>%
  features(difference(drugSales), unitroot_nsdiffs)

```

## Are we good now?

```{r}
plotDiaSeasonalDiffACF <-
  tsDia %>%
  mutate(diffDrugSalesthenDiffSeason = difference(difference(drugSales), 12)) %>%
  PACF(diffDrugSalesthenDiffSeason, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the antidiabetic drug sales data")
plotDiaSeasonalDiffACF

```

## Our friend KPSS says so:

```{r}
tsDia %>%
  mutate(diffDrugSalesthenDiffSeason = difference(difference(drugSales), 12)) %>%
  features(diffDrugSalesthenDiffSeason, unitroot_kpss)

```

## What if we transformed?

```{r}
plotDiaSeasonalDiffACF <-
  tsDia %>%
  mutate(logDrugSalesSeasonthenDiff = difference(difference(log(drugSales)), 12)) %>%
  PACF(logDrugSalesSeasonthenDiff, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the antidiabetic drug sales data")
plotDiaSeasonalDiffACF

```

## Are we still friends with KPSS?

```{r}
tsDia %>%
  mutate(logDrugSalesSeasonthenDiff = difference(difference(log(drugSales)), 12)) %>%
  features(logDrugSalesSeasonthenDiff, unitroot_kpss)

```


Rule of thumb not to overfit (Don't believe rules of thumb):
- If the correlation at the seasonal period is positive, add a SAR term
- If negative, add a SMA term
- Avoid mixing SAR and SMA in the same model
- Avoid using more than one of either

## ARIMA ARIMA!

```{r}
fitDiaARIMA <-
  tsDia %>%
  model(fitArima = ARIMA(drugSales ~ PDQ(0,1,1),
              stepwise = FALSE, approximation = FALSE))
report(fitDiaARIMA)

```

## Cross-validation in time series using ARIMA

### DO NOT RUN THIS!

```{r}
# set.seed(333)
# tsDiaCV <-
#   tsDia %>%
#   slice(1:(n()-12)) %>%
#   stretch_tsibble(.init = 12) %>%
#   model(ARIMA(drugSales)) %>% # ~ pdq(4,1,1) + PDQ(0,1,1)
#   forecast(h = 12) #%>%
#   #accuracy(tsDia)

```

### DO NOT RUN THIS!

```{r}
# tsDiaCV <- 
#   tsDiaCV %>%
#   group_by(.id) %>%
#   mutate(h = row_number()) %>%
#   ungroup()

# saveRDS(tsDiaCV, 'tsDiaCV.rds')

```

### DO NOT RUN THIS!

```{r}
tsDiaCV <- readRDS('tsDiaCV.rds')

plottsDiaCV <- 
  tsDiaCV %>% 
  accuracy(tsDia, by = 'h') %>% 
  ggplot(aes(x = h, y = RMSE)) + geom_point() +
        scale_x_continuous(name = " ", breaks = c(1:12))
ggplotly(plottsDiaCV)

```

# Training models and making predictions
# [SLIDES LEFT TO THURSDAY]

## Remember U.S. consumption data

```{r}
plotEconDecomposed <- 
  tsEcon %>%
  model(STL(Consumption ~ trend() + season(window='periodic'), robust = TRUE)) %>% 
  components() %>%
  autoplot() +
  xlab("Year (quarterly data)") + ylab("Percentage changes in personal consumption") +
  ggtitle("Seasonal and Trend decomposition using Loess (STL) for U.S. consumption data") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")
plotEconDecomposed

```

## ACF for the U.S. consumption

```{r}
plotEconACF <-
  tsEcon %>%
  ACF(Consumption, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the U.S. personal consumption data")
plotEconACF

```

## ACF for the U.S. consumption after differencing

```{r}
plotEconDiffACF <-
  tsEcon %>%
  mutate(diffConsumption = difference(Consumption)) %>%
  ACF(diffConsumption, lag_max = 48) %>%
  autoplot() +  ggtitle("Autocorrelation function (ACF) plot for the U.S. personal consumption data")
plotEconDiffACF

```

## Are we in line with the unit root test?

```{r}
tsEcon %>%
  features(Consumption, unitroot_ndiffs)

tsEcon %>%
  features(Consumption, unitroot_nsdiffs)

```

## What about the KPSS test?

```{r}
tsEcon %>%
  features(Consumption, unitroot_kpss)

tsEcon %>%
  features(difference(Consumption), unitroot_kpss)

```

## ARIMA model for the U.S. consumption

```{r}
fitEconARIMA <-
  tsEcon %>%
  model(fitArima = ARIMA(Consumption ~ PDQ(0,0,0), #pdq(3,0,0) + 
              stepwise = FALSE, approximation = FALSE)
  )
report(fitEconARIMA)

```

## Residual diagnostics and Ljung-Box test for the independence of residuals

```{r}
fitEconARIMA %>% gg_tsresiduals()

fitEconARIMA %>% 
  augment() %>%
  features(.resid, ljung_box, 
           lag = 8, dof = 4)

```

## ARIMA regression with the additional features/predictors included

```{r}
fitEconARIMAOthers <-
  us_change %>%
  model(fitArima = ARIMA(Consumption ~ pdq(3,0,0) + PDQ(0,0,0) + Income + Savings + Unemployment))
report(fitEconARIMAOthers)

```

## ARIMA regression with the additional features/predictors included (again)

```{r}
fitEconARIMAOthersGridAgain <-
  us_change %>%
  model(fitArima = ARIMA(Consumption ~ PDQ(0,0,0) + Income + Savings + Unemployment, stepwise = FALSE, approximation = FALSE)) #pdq(2,1,4) + 
report(fitEconARIMAOthersGridAgain)

```

## What about the p-values?

```{r}
# p-value for Income
# t-statistic for Income is 0.7503/0.0388 = 19.33763
2*pt(-abs(0.7503/0.0388), nrow(tsEcon)-9)

# p-values for Savings and Unemployment:
2*pt(-abs(-0.0560/0.0029), nrow(tsEcon)-9)
2*pt(-abs(-0.2737/0.0676), nrow(tsEcon)-9)

```

## Comparing residual diagnostics tests across the ARIMA models

```{r}
fitEconARIMA %>% gg_tsresiduals()
fitEconARIMAOthers %>% gg_tsresiduals()
fitEconARIMAOthersGridAgain %>% gg_tsresiduals()

```

## More models trained and run on test data for predictions to be evaluated/compared

```{r}
tsEconFitAll <-
  tsEconTrain %>%
  model(
    model1TimeTrendAndSeason = TSLM(Consumption ~ trend() + season()),
    model2TimeTrend = TSLM(Consumption ~ trend()),
    model3OtherFeatures = TSLM(Consumption ~ Income + Savings + Unemployment),
    model4TimeTrendAndOthers = TSLM(Consumption ~ trend() + Income + Savings + Unemployment),
    model5TimeTrendAndOthersKnot = TSLM(Consumption ~ trend(knots = c(1980)) + Income + Savings + Unemployment),
    model6ARIMABase300 = ARIMA(Consumption ~ pdq(3,0,0) + PDQ(0,0,0)),
    model7ARIMAOthers300 = ARIMA(Consumption ~ pdq(3,0,0) + PDQ(0,0,0) + Income + Savings + Unemployment),
    model8ARIMAOthers214 = ARIMA(Consumption ~ 1 + pdq(2,1,4) + PDQ(0,0,0) + Income + Savings + Unemployment)#,
    #model8ARIMAOthers510 = ARIMA(Consumption ~ 1 + pdq(5,1,0) + PDQ(0,0,0) + Income + Savings + Unemployment)
  )

tsEconPredictAll <-
  tsEconFitAll %>%
  forecast(new_data = tsEconTest)

accuracy(tsEconPredictAll, tsEconTest)

```

## Regression and ARIMA predictive modeling compared (Train/Test split)

```{r}
plotEconAllPredicted #Model #5

plotEconAllPredictedARIMA <-
  us_change %>%
  filter(Quarter < '2011-01-01') %>%
  model(ARIMA(Consumption ~ 1 + pdq(2,1,4) + PDQ(0,0,0) + Income + Savings + Unemployment)) %>%
  forecast(new_data = us_change %>% filter(Quarter >= '2011-01-01')) %>%
  autoplot(us_change, colour = "#960A0A") + #level = NULL,
  geom_line(colour = '#535353') +
  xlab("Year (quarterly data)") + ylab("Percentage changes in personal consumption") +
  ggtitle("U.S. personal consumption data")
plotEconAllPredictedARIMA

```

# Anomaly detection in time series using STL and IQR
```{r}
date(tsDia$month)

tsDia
```
```{r}
anomalyDia$month
```


```{r}
library(anomalize)

anomalyDia <- 
  tsDia %>%
  mutate(month = date(month)) %>%
  time_decompose(drugSales, method = "stl") %>%
  anomalize(remainder, method = "iqr") %>%
  plot_anomalies() +
  labs(title = "Anomaly detection for the antidiabetic drug sales data") +
  xlab("Year") + ylab("Total prescriptions ($ million)") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")

anomalyDia

```

# Anomaly detection in time series using STL and IQR in the decomposition plot

```{r}
anomalyDiaDecompose <- 
  tsDia %>%
  mutate(month = date(month)) %>%
  time_decompose(drugSales, method = "stl") %>%
  anomalize(remainder, method = "iqr") %>%
  plot_anomaly_decomposition() +
  labs(title = "Anomaly detection for the antidiabetic drug sales data") +
  xlab("Year") + ylab("Total prescriptions ($ million)") +
  scale_x_date(date_breaks = "years" , date_labels = "%y")

anomalyDiaDecompose

```


